Differential Expression - MSSM-Penn-Pitt - DLPFC - Dx

### 2020-08-25 individual-cohorts/split_by_analysis/HBCC_dsACC_DE_Diagnosis.Rmd
remove samples based on age threshold - all cohorts

# Download CQN counts
CQN_ID = "syn22086076"
ALL_USED_IDs = c(CQN_ID)
CQN.GENE_EXPRESSION = downloadFile(CQN_ID) %>% 
  tibble::column_to_rownames(var = "ensembl_gene_id") %>% 
  data.matrix()

@@

>>>>

# Download CQN counts
CQN_ID = "syn22086076"
ALL_USED_IDs = c(CQN_ID)
CQN.GENE_EXPRESSION = downloadFile(CQN_ID) %>% 
  tibble::column_to_rownames(var = "ensembl_gene_id")

@@

# Remove ages under 17
COVARIATES <- COVARIATES[COVARIATES$ageOfDeath >= 17,]
NEW.COUNTS <- NEW.COUNTS[names(NEW.COUNTS) %in% rownames(COVARIATES)]
CQN.GENE_EXPRESSION <- CQN.GENE_EXPRESSION[names(CQN.GENE_EXPRESSION) %in% rownames(COVARIATES)] %>% 
  data.matrix()

### 2020-08-25 individual-cohorts/split_by_analysis/MSSM-Penn-Pitt_ACC_DE_Diagnosis.Rmd
remove samples based on age threshold - all cohorts

# Download CQN counts
CQN_ID = "syn22013154"
ALL_USED_IDs = c(CQN_ID)
CQN.GENE_EXPRESSION = downloadFile(CQN_ID) %>% 
  tibble::column_to_rownames(var = "ensembl_gene_id") %>% 
  data.matrix()

>>>>

# Download CQN counts
CQN_ID = "syn22013154"
ALL_USED_IDs = c(CQN_ID)
CQN.GENE_EXPRESSION = downloadFile(CQN_ID) %>% 
  tibble::column_to_rownames(var = "ensembl_gene_id")

### 2020-08-25 individual-cohorts/split_by_analysis/MSSM-Penn-Pitt_DLPFC_DE_Diagnosis.Rmd
remove samples based on age threshold - all cohorts

# Download CQN counts
CQN_ID = "syn22045741"
ALL_USED_IDs = c(CQN_ID)
CQN.GENE_EXPRESSION = downloadFile(CQN_ID) %>% 
  tibble::column_to_rownames(var = "ensembl_gene_id") %>% 
  data.matrix()

>>>>

# Download CQN counts
CQN_ID = "syn22045741"
ALL_USED_IDs = c(CQN_ID)
CQN.GENE_EXPRESSION = downloadFile(CQN_ID) %>% 
  tibble::column_to_rownames(var = "ensembl_gene_id")
